Summary of the things that I learned

### 2024-12-09 600-paper.tex
Improve the diagram on the front of the thesis

Recall that we have an equivalence $ [\op{C_{A_1}}, \SET] \simeq \RAct{A_1} $.

\begin{remark}\label{rem:ract-presheaf-equivalence}
  Note that, like in the last chapter, $ \R_A $ pops up as the Karoubi envelope of the monoid category $ \C_{A_1} $, and fits into the following diagram:
  \begin{center}
    \begin{tikzcd}
      & \C_{A_1} \arrow[d, hookrightarrow, "\yo"] \arrow[r, hookrightarrow, "\iota_{C_{A_1}}"] & \R_A \arrow[d, hookrightarrow, "\yo"]\\
      \RAct{A_1} & P \C_{A_1} \arrow[l, "\sim"] & P \R_A \arrow[l, "\sim"]
    \end{tikzcd}
  \end{center}
  Explicitly, this gives the embedding $ \R_A(\mathbf 1_1, -): \R_A \hookrightarrow \RAct{A_1} $ given by
  \[ X \mapsto \R_A(\mathbf 1_1, X) = \{ x : A \mid X \circ x = x \}. \]
  Also, note that if $ A = L_0 $ for some $ \lambda $-theory $ L $, then the monoid $ A_1 $ is equivalent to the monoid $ L_1 $, and $ \R_A $ is equivalent to our familiar category of retracts $ \R $. Using Lemma \ref{lem:equivalent-presheaf-cats}, we have the following 2-commutative diagram:
  \begin{center}
    \begin{tikzcd}
      &
      \C_{{L_0}_1} \arrow[dd, "\yo" description, near start, hook] \arrow[rrr, "\iota_{C_{{L_0}_1}}" description, hook] \arrow[rd, "\sim" description, no head] & & & \R_{L_0} \arrow[dd, "\yo" description, near start, hook] \arrow[rd, "\sim" description, no head] & & \\
      &
      & \C_{L_1} \arrow[dd, "\yo" description, near start, hook] \arrow[r, hook] & \mathbf L \arrow[rr, hook] \arrow[dd, "\yo" description, near start, hook] & & \mathbf R \arrow[dd, "\yo" description, near start, hook] \arrow[rdd, hook] & \\
      \RAct{{L_0}_1} &
      P \C_{{L_0}_1} \arrow[l, "\sim"'] \arrow[rd, "\sim" description, no head] & & & P \R_{L_0} \arrow[lll, "\sim" description] \arrow[rd, "\sim" description, no head] & & \\
      &
      & P \C_{L_1} & P \mathbf L \arrow[l, "\sim" description] & & P \R \arrow[ll, "\sim" description] & \Pshf L \arrow[lll, "\sim" description, bend left]
    \end{tikzcd}
  \end{center}
\end{remark}

>>>>

Recall that we have an equivalence $ [\op{\C_{A_1}}, \SET] \simeq \RAct{A_1} $.

\begin{remark}\label{rem:ract-presheaf-equivalence}
  Note that, like in the last chapter, $ \R_A $ pops up as the Karoubi envelope of the monoid category $ \C_{A_1} $, and fits into the following diagram:
  \begin{center}
    \begin{tikzcd}
      & \C_{A_1} \arrow[d, hookrightarrow, "\yo"] \arrow[r, hookrightarrow, "\iota_{\C_{A_1}}"] & \R_A \arrow[d, hookrightarrow, "\yo"]\\
      \RAct{A_1} & P \C_{A_1} \arrow[l, "\sim"] & P \R_A \arrow[l, "\sim"]
    \end{tikzcd}
  \end{center}
  Explicitly, this gives the embedding $ \R_A(\mathbf 1_1, -): \R_A \hookrightarrow \RAct{A_1} $ given by
  \[ X \mapsto \R_A(\mathbf 1_1, X) = \{ x : A \mid X \circ x = x \}. \]
  Also, note that if $ A = L_0 $ for some $ \lambda $-theory $ L $, then the monoid $ A_1 $ is equivalent to the monoid $ L_1 $, and $ \R_A $ is equivalent to our familiar category of retracts $ \R $. Using Lemma \ref{lem:equivalent-presheaf-cats}, we have the following 2-commutative diagram:
  \begin{center}
    \begin{tikzcd}
      &
      \C_{{L_0}_1}
        \arrow[dd, "\yo" description, near start, hook]
        \arrow[rrr, "\iota_{\C_{{L_0}_1}}" description, hook]
        \arrow[rd, "\sim" description, no head] & & &
      \R_{L_0}
        \arrow[dd, "\yo" description, near start, hook]
        \arrow[rd, "\sim" description, no head] & & \\ & &
      \C_{L_1}
        \arrow[r, hook] &
      \L & &
      \R
        \arrow[from=ll, hook, crossing over]
        \arrow[dd, "\yo" description, near start, hook]
        \arrow[rdd, hook] & \\
      \RAct{{L_0}_1} &
      P \C_{{L_0}_1}
        \arrow[l, "\sim"']
        \arrow[rd, "\sim" description, no head] & & &
      P \R_{L_0}
        \arrow[lll, "\sim" description]
        \arrow[rd, "\sim" description, no head] & & \\ & &
      P \C_{L_1}
        \arrow[from=uu, "\yo" description, near start, hook, crossing over] &
      P \mathbf L
        \arrow[from=uu, "\yo" description, near start, hook, crossing over]
        \arrow[l, "\sim" description] & &
      P \R
        \arrow[ll, "\sim" description] &
      \Pshf L
        \arrow[lll, "\sim" description, bend left]
    \end{tikzcd}
  \end{center}
\end{remark}
